The landscape of chloroplast genome assembly tools

### 2019-05-20 bmc_article.tex
Update on Overleaf.

\[ score = 1 - \frac{1}{4} \cdot \left( |1- cov_{ref}| +  |1- cov_{qry}| + \left|1- e^{-\left| \ln{\frac{cov_{qry}}{cov_{ref}}}\right|}\right| + \left| 1 - \frac{1}{n_{contigs}} \right| \right) \]

Ich glaube diese Formel lässt sich vereinfachen zu:
\[ score = \frac{1}{4} \cdot \left( cov_{ref} +  cov_{qry} + e^{-\left| \ln{\frac{cov_{qry}}{cov_{ref}}}\right|} + \frac{1}{n_{contigs} }\right) \]

@@

\begin{figure}[h!]
  \includegraphics[width=\textwidth]{plots/usage_amount_threads.pdf}
  \caption{\csentence{Sample figure title.}
      Figure legend text.}
      \end{figure}

\begin{figure}[h!]
  \includegraphics[width=\textwidth]{plots/sim_tiles.pdf}
  \caption{\csentence{Sample figure title.}
      Figure legend text.}
      \end{figure}

\begin{figure}[h!]
  \includegraphics[width=\textwidth]{plots/repro.pdf}
  \caption{\csentence{Scatterplot of scores between two independent runs for reproducibility testing}
      Figure legend text.}
      \end{figure}

\begin{figure}[h!]
  \includegraphics[width=\textwidth]{plots/comp_time_log.pdf}
  \caption{\csentence{Sample figure title.}
      Figure legend text.}
      \end{figure}

\begin{figure}[h!]
  \includegraphics[width=\textwidth,page=2]{plots/upset.pdf}
  \caption{\csentence{Sample figure title.}
      Figure legend text.}
      \end{figure}

\begin{figure}[h!]
  \includegraphics[width=\textwidth]{plots/real_datasets_tree.pdf}
  \caption{\csentence{Sample figure title.}
      Figure legend text.}
      \end{figure}

>>>>

\[ score = \frac{1}{4} \cdot \left( cov_{ref} +  cov_{qry} + e^{-\left| \ln{\frac{cov_{qry}}{cov_{ref}}}\right|} + \frac{1}{n_{contigs} }\right) \]

% equivalenter Vorschlag mit min anstatt e^ln

\[ score = \frac{1}{4} \cdot \left( cov_{ref} +  cov_{qry} + min\left\{ \frac{cov_{qry}}{cov_{ref}}, \frac{cov_{ref}}{cov_{qry}}\right\} + \frac{1}{n_{contigs} }\right) \cdot 100  \]

@@

\begin{figure}[h!]
  \includegraphics[width=\textwidth]{plots/usage_amount_threads.pdf}
  \caption{\csentence{Performance metrics}
      Boxplots depictiing the demand of CPU and RAM and disk space needed depending on the assembler, input data size and number of threads}
      \end{figure}

\begin{figure}[h!]
  \includegraphics[width=\textwidth]{plots/sim_tiles.pdf}
  \caption{\csentence{Score of assemblies on simulated data}
      Figure legend text.}
      \end{figure}

\begin{figure}[h!]
  \includegraphics[width=\textwidth]{plots/repro.pdf}
  \caption{\csentence{Scores between two independent runs for reproducibility testing}
      }
      \end{figure}

\begin{figure}[h!]
  \includegraphics[width=\textwidth]{plots/comp_time_log.pdf}
  \caption{\csentence{Computation time depending on number of threads and size of input data}
  }
      \end{figure}

\begin{figure}[h!]
  \includegraphics[width=\textwidth,page=2]{plots/upset.pdf}
  \caption{\csentence{Upset plot \cite{lex2014upset} comparing success of assemblers on the real data sets}
      The plot shows the intersection of success ($score > 99$) between assemblers. For 69 datasets only \go{} was able to obtain a complete chloroplast. 43 were successful with both \go{} and \fp{} and so on}
      \end{figure}

\begin{figure}[h!]
  \includegraphics[width=\textwidth]{plots/real_datasets_tree.pdf}
  \caption{\csentence{Sucess of assemblers on real data sets on tree derived from ncbi taxonomy \cite{ncbi2011}}
      Figure legend text.}
      \end{figure}
